\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Zain Aftab}}\\
	Lahore, Pakistan $\cdot$ zainaftab44@gmail.com $\cdot$ +92 312 4210568 $\cdot$ https://www.linkedin.com/in/zainaftab\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{PUCIT, University of the Punjab}\hfill Lahore, PK\\
BS Computer Science \hfill Oct 2011 - Jul 2015\\
\vspace{2mm}
\textbf{PUCIT, University of the Punjab}\hfill Lahore, PK\\
MPhil Computer Science \hfill Sep 2015 - July 2017\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Contour Software} \hfill Lahore, PK\\
\textit{Software Developer} \hfill Feb 2020 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Managing the software build, release and deployment process.
	\item Integrated the system with Zapier for automation purposes.
	\item Analysis and execution of ETL for migration of legacy system users to latest release.
	\item Developing and integrating new features and maintained existing ones.
	\item Performing code reviews to improve code quality.
\end{itemize}
\textbf{BellStone Pvt Ltd} \hfill Lahore, PK\\
\textit{Software Developer} \hfill Oct 2018 - Dec 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Leading the R\&D team for performing live data transfer
	\item Fullstack development of application using Node.js, HTML/CSS/JS, JQuery and WebRTC stack
	\item Integration with third-party payment service
	\item Benchmarking application performance against opensource systems.
	\item Integrated mailgun for email sending to users for verification and notifications.
\end{itemize}
\textbf{Sir Syed College of Computer Science} \hfill Lahore, PK\\
\textit{Lecturer} \hfill Jan 2017 - Oct 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Teaching software development courses
	\item Supervised Final Year Projects.
	\item Worked as part of Accreditation Committee
	\item Represented college at various events and workshops
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Languages:           & PHP, Node.js, JavaScript, Java             \\
	Frameworks:          & Zend Framework, Laravel, Kohana, ExpressJs \\
	Databases:           & MySQL, MongoDB, PostgreSQL                 \\
	Software Versioning: & SVN, Git                                   \\
	Misc:                & Docker, Linux, MVC                         \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Zurple}} {\sl PHP, Java, Zend Framework, Javascript, MySQL} \hfill https://zurple.com/\\
Zurple software offers a complete real estate marketing solution for busy agents. The defining feature of zurple is automated lead engagement for our agents.\\
\vspace*{2mm}
{\textbf{TorchX}} {\sl PHP, Java, Zend Framework, Javascript, jQuery, MySQL} \hfill https://torchx.com/\\
TORCHx is a premium digital marketing platform designed to help residential Real Estate Agents and Brokers generate leads and never let them fall through the cracks.\\
\vspace*{2mm}
{\textbf{PropertyPulse}} {\sl PHP, Kohana, Wordpress, jQuery, Facebook Ads, MySQL} \hfill https://propertypulse.info/\\
PropertyPulse is developed to provide all the real estate professionals out there looking for the best and easiest method of advertising themselves on new age mediums with an intelligent solution.\\
\vspace*{2mm}
{\textbf{Trango}} {\sl WebRTC, Node.js, ExpressJs, MySQL} \hfill https://play.google.com/store/apps/details?id=com.bellstone.trango\\
Trango is a live file transfer, video call and voice calling application. It auto-discovers user availability in locat network and internet. Trango is much faster, faithfully secure and substantially cheaper than antiquated alternatives like intercom/pbx.\\
\vspace*{2mm}



\ 
\end{document}